---
title: "Credit Risk Modeling in RStudio"
resource_files:
- config.yml
output: html_notebook
---

### Predicting Defaults on Credit Card Payments

This model will predict the probability that a credit card holder will default on their payment given their payment history and demographic information.

Load libraries:

```{r message=FALSE}
library(readxl)
library(xgboost)
library(caTools)
library(config)
```

Load config file:

```{r}
model_config <- get("model_config")
```

This notebook refers to **`r model_config$id`**.

### Load data

Load the data and view its contents:

```{r}
# Data from https://archive.ics.uci.edu/ml/datasets/default+of+credit+card+clients
df <- read_excel("data/default-of-credit-card clients.xls", skip = 1)
df
```

### Split data into training and testing sets

Split the data set into 80% training and 20% testing portions:

```{r warning=FALSE}
set.seed(123)
sample <- sample.split(df, SplitRatio = 0.80)

train <- as.matrix(subset(df, sample == TRUE))
x_train <- train[,-25]
y_train  <- train[, 25, drop=FALSE]

test <- as.matrix(subset(df, sample == FALSE))
x_test <- test[,-25]
y_test  <- test[, 25, drop=FALSE]
```

### Train model

Train the model using a binary classification algoritm:

```{r}
bst <- xgboost(data = x_train,
               label = y_train,
               max.depth = 2,
               eta = 1,
               nthread = 2,
               nrounds = 2,
               booster = "gbtree",
               objective = "binary:logistic")
```

Show the most important factors and their weights:

```{r}
imp_matrix <- xgb.importance(feature_names = colnames(x_train), model = bst)
xgb.plot.importance(importance_matrix = imp_matrix)
```

### Serialize model

Serialize the trained model to a file for later use:

```{r}
model_save_path = paste0(model_config$path_prefix, model_config$id, model_config$path_suffix)
xgb.save(bst, model_save_path)
```

### Generate model predictions

Generate model predictions on the test data:

```{r}
pred <- predict(bst, x_test)
```

### Score model

Calculate the accuracy of the model:

```{r}
err <- mean(as.numeric(pred > 0.5) != y_test)
print(paste("Test Accuracy =", 1-err))
```

### Test model predictions

Generate a prediction for an account that we know has a good payment history:

```{r}
test_data <- matrix(c(35, 500000, 1, 1, 1, 58, -2, -2, -2, -2, -2, -2, 13709, 5006, 31130, 3180, 0, 5293, 5006, 31178, 3180, 0, 5293, 768), nrow = 1)
pred_good <- predict(bst, test_data)
pred_good
```

This account has a `r pred_good` probability of defaulting on their payment.

---

Generate a prediction for an account that we know defaults on their payment:

```{r}
test_data <- matrix(c(1, 20000, 2, 2, 1, 24, 2, 2, -1, -1, -2, -2, 3913, 3102, 689, 0, 0, 0, 0, 689, 0, 0, 0, 0), nrow = 1)
pred_bad <- predict(bst, test_data)
pred_bad
```

This account has a `r pred_bad` probability of defaulting on their payment.
